msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-12 paper.tex
Move arg section next to recombination.
Add ARG comparison plot.

\documentclass{article}
\usepackage[round]{natbib}
\usepackage{listings}
\usepackage[english]{babel}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{geometry}%
\usepackage{color}
\usepackage{dsfont}
\usepackage{verbatim}%
\usepackage{environ}%
\usepackage[right]{lineno}%
%\usepackage{showkeys}

@@

\begin{figure}
\caption{\label{fig-recombination-perf}Approximate run time for \msprime\
simulations as a function of scaled recombination rate.}
\end{figure}

>>>>

\documentclass{article}
\usepackage[round]{natbib}
\usepackage{listings}
\usepackage[english]{babel}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{geometry}%
\usepackage{color}
\usepackage{graphicx}
\usepackage{dsfont}
\usepackage{verbatim}%
\usepackage{environ}%
\usepackage[right]{lineno}%
%\usepackage{showkeys}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/recombination}
\caption{\label{fig-recombination-perf}(A) Approximate run time for \msprime\
simulations as a function of scaled recombination rate.
(B) Comparison of the ARG simulations vs minimal tree sequence representation.}
\end{figure}
